Machine learning topological phases in real space

### 2020-07-27 07_paper/article.tex
Generated version of paper without buggy macros

%\documentclass[aps,prb,amsmath,twocolumn,amssymb,titlepage]{revtex4-1}
\documentclass[10pt]{revtex4-1}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{nicefrac}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{amsmath} 
\usepackage{subfigure}
\usepackage{multirow} 
\usepackage{tabularx} 
\usepackage{array}
\usepackage{units}
\usepackage{tensor} 
\usepackage{braket}
\usepackage{bm}
\usepackage{hyperref}
\usepackage[resetlabels, labeled]{multibib}
\usepackage{xcolor}
\usepackage{bbm}
\usepackage{xfp}
\usepackage[labelfont=bf,textfont=md,justification=raggedright,font=footnotesize]{caption}
\usepackage{booktabs}
\renewcommand{\figurename}{Figure}
\renewcommand{\tablename}{Table}
\renewcommand{\thetable}{\arabic{table}}
%\captionsetup{justification=raggedright, singlelinecheck = false}
%\usepackage{makecell}
%\usepackage{cellspace}

%\newcites{supp}{References}

%\def\basiceval#1{\the\numexpr#1\relax}

@@

\newcommand{\hc}{^{\dagger}}
\newcommand{\ad}{\operatorname{{\mathrm ad}}}
\newcommand{\adn}{\ad_{\hat n}}
\newcommand{\adx}{\ad_{\hat x}}
\newcommand{\adX}[1][]{\ad_{\hat {\mathbf{X}}_{#1}}}
\newcommand{\adp}{\ad_{\hat p}}
\newcommand{\calD}{\mathcal{D}}    %Caligraphic D
\newcommand{\inbk}[1]{\left[ #1 \right]}
\newcommand{\inbr}[1]{\left\{ #1 \right\}}
\newcommand{\inp}[1]{\left( #1 \right)}
\newcommand{\pd}{\partial}
\newcommand{\pdf}[3]{\frac{\pd^{#1} #2}{\pd #3^{#1}}} %Partial derivative
\newcommand{\fdf}[3][]{\frac{\delta^{#1} #2}{\delta #3^{#1}}} %Functional derivative

%ssh1

%Our test set in this experiment contained 1005 Hamiltonians (approx. 15.3\% of all data). Of the remaining 5556 Hamiltonians, 556 were %randomly assigned to the training set (approx. 8.5\%) and 5000 (approx. 76.2\%) were used to compute validation scores at each iteration. %These proportions between training and validation sets are such that approximately 10\%  of Hamiltonians from outside of the test set were %used for training at each iteration. The composition of the train + validation set for this experiment was 50.8\% of Hamiltonians with %winding number $W$ = 0 and 49.2\% with winding number $W$ = 1. The composition of the test set was 44.8\% of Hamiltonians with winding number %$W$ = 0 and 55.2\% with winding number $W=1$. \textcolor{blue}{Our learning algorithm of choice for this experiment was a simple decision %tree model \cite{breiman2017classification}}.\citequote{eigenvector_ensembling_alg}

%\documentclass{article}
%\usepackage{xfp}

%\begin{document}

%\fpeval{31/45}

%\fpeval{round(31/45,5)}

%\end{document}
\newcommand{\indicator}[1]{\mathbbm{1}_{\mathcal{#1}}}
%%%%%% Numerical experiments parameters
\newcommand\nPrec{2}    % precision digits
\newcommand\accPrec{4}  % precision digits for accuracy scores
\newcommand\nHam{6561}  % total number of hamiltonians
\newcommand\epsilonValue{0.01}  % epsilon criterium for test set
\newcommand\nExp{100}   % number of experiments
%%%table commands
%\newcommand{\tableRow}[1]{\\[#1 cm]\hline} %deprecated table row, but might be useful
\newcommand{\tableRow}[1]{\\[#1 cm]}
\newcommand{\tableRowHeader}[1]{\\[#1 cm]\hline}
\newcommand\tableRowHeaderEnd{\tableRowHeader{0.3}}
\newcommand\tableRowEnd{\tableRow{0.15}}
%\newcommand\SSHSys{\thead{SSH systems}}         deprecated, might be useful
%\newcommand\Feat{\thead{Features}}              deprecated, might be useful
%\newcommand\ValEig{\thead{Val. eigenvectors}}   deprecated, might be useful
%\newcommand\TestEig{\thead{Test eigenvectors}}  deprecated, might be useful
%\newcommand\ValHam{\thead{Val. Hamiltonians}}   deprecated, might be useful
%\newcommand\TestHam{\thead{Test Hamiltonians}}  deprecated, might be useful
\newcommand\SSHSys{SSH system}         
\newcommand\Feat{Features}              
\newcommand\ValEig{Val. eigenvectors}   
\newcommand\TestEig{Test eigenvectors}  
\newcommand\ValHam{Val. Hamiltonians}   
\newcommand\TestHam{Test Hamiltonians}

%%%%%%%%%%%%%%% ssh1 experiments
%%% data statistics
\newcommand\sshOneTrainNHam{556}
\newcommand\sshOneTrainFracHam{\fpeval{round(\sshOneTrainNHam/\nHam*100,\nPrec)}}
\newcommand\sshOneValNHam{5000}
\newcommand\sshOneValFracHam{\fpeval{round(\sshOneValNHam/\nHam*100,\nPrec)}}
\newcommand\sshOneTrainPlusValNHam{\fpeval{\sshOneTrainNHam+\sshOneValNHam}}
\newcommand\sshOneTestNHam{1005}
\newcommand\sshOneTestFracHam{\fpeval{round(\sshOneTestNHam/\nHam*100,\nPrec)}}
\newcommand\sshOneTrainPlusValWindZeroNHam{2822} %number of winding = 0 in train+val set
\newcommand\sshOneTrainPlusValWindZeroFracHam{\fpeval{round(\sshOneTrainPlusValWindZeroNHam/(\sshOneTrainNHam+\sshOneValNHam)*100,\nPrec)}}
\newcommand\sshOneTrainPlusValWindOneNHam{2734}  %number of winding = 1 in train+val set
\newcommand\sshOneTrainPlusValWindOneFracHam{\fpeval{round(\sshOneTrainPlusValWindOneNHam/(\sshOneTrainNHam+\sshOneValNHam)*100,\nPrec)}}
\newcommand\sshOneTestWindZeroNHam{378}      %number of winding = 0 in test set
\newcommand\sshOneTestWindOneNHam{466}       %number of winding = 1 in test set
\newcommand\sshOneTestWindZeroFracHam{\fpeval{round(\sshOneTestWindZeroNHam/(\sshOneTestWindZeroNHam+\sshOneTestWindOneNHam)*100,\nPrec)}}
\newcommand\sshOneTestWindOneFracHam{\fpeval{round(\sshOneTestWindOneNHam/(\sshOneTestWindZeroNHam+\sshOneTestWindOneNHam)*100,\nPrec)}}
%%% real space accuracies
%\newcommand\sshOneEigenTrainAcc{0.981438129496403}       % eigenvector training accuracy
%\newcommand\sshOneEigenValAcc{0.96392276}         % eigenvector val accuracy
%\newcommand\sshOneEigenTestAcc{0.78966836492891}        % eigenvector test accuracy
%\newcommand\sshOneHamTrainAcc{1.0}             % Hamiltonian training accuracy
%\newcommand\sshOneHamValAcc{1.0}               % Hamiltonian val accuracy
%\newcommand\sshOneHamTestAcc{0.9918720379146919}          % Hamiltonian test accuracy
%\newcommand\sshOneHamTestBaseline{\fpeval{round(\sshOneTestWindOneNHam/(\sshOneTestWindZeroNHam+\sshOneTestWindOneNHam),\accPrec)}}

%%% ssh1 baseline accuracy
\newcommand\sshOneHamTestBaseline{\fpeval{round(\sshOneTestWindOneNHam/(\sshOneTestWindZeroNHam+\sshOneTestWindOneNHam),\accPrec)}}

@@

\newcommand\xOneEigTrain{\fpeval{round(0.981438129496403,\accPrec)}}
\newcommand\xOneEigVal{\fpeval{round(0.96392276,\accPrec)}}
\newcommand\xOneEigTest{\fpeval{round(0.78966836492891,\accPrec)}}
\newcommand\xOneHamTrain{\fpeval{round(1.0,\accPrec)}}
\newcommand\xOneHamVal{\fpeval{round(1.0,\accPrec)}}
\newcommand\xOneHamTest{\fpeval{round(0.9918720379146919,\accPrec)}}

@@

\newcommand\xSOneEigTrain{\fpeval{round(0.9699771582733813,\accPrec)}}
\newcommand\xSOneEigVal{\fpeval{round(0.9444134200000001,\accPrec)}}
\newcommand\xSOneEigTest{\fpeval{round(0.7763444312796207,\accPrec)}}
\newcommand\xSOneHamTrain{\fpeval{round(0.9880395683453237,\accPrec)}}
\newcommand\xSOneHamVal{\fpeval{round(0.9853300000000002,\accPrec)}}
\newcommand\xSOneHamTest{\fpeval{round(0.9904502369668248,\accPrec)}}

@@

\newcommand\xcOneEigTrain{\fpeval{round(0.9753276978417266,\accPrec)}}
\newcommand\xcOneEigVal{\fpeval{round(0.9521145999999999,\accPrec)}}
\newcommand\xcOneEigTest{\fpeval{round(0.7373592417061612,\accPrec)}}
\newcommand\xcOneHamTrain{\fpeval{round(0.9982553956834532,\accPrec)}}
\newcommand\xcOneHamVal{\fpeval{round(0.9975820000000002,\accPrec)}}
\newcommand\xcOneHamTest{\fpeval{round(0.9916232227488153,\accPrec)}}

@@

\newcommand\xcEOneEigTrain{\fpeval{round(0.9755357913669066,\accPrec)}}
\newcommand\xcEOneEigVal{\fpeval{round(0.8280291200000001,\accPrec)}}
\newcommand\xcEOneEigTest{\fpeval{round(0.6066537914691943,\accPrec)}}
\newcommand\xcEOneHamTrain{\fpeval{round(0.998525179856115,\accPrec)}}
\newcommand\xcEOneHamVal{\fpeval{round(0.997906,\accPrec)}}
\newcommand\xcEOneHamTest{\fpeval{round(0.9190876777251185,\accPrec)}}

@@

\newcommand\xcSEOneEigTrain{\fpeval{round(0.9701161870503597,\accPrec)}}
\newcommand\xcSEOneEigVal{\fpeval{round(0.9444223399999998,\accPrec)}}
\newcommand\xcSEOneEigTest{\fpeval{round(0.8176174170616113,\accPrec)}}
\newcommand\xcSEOneHamTrain{\fpeval{round(0.9882014388489206,\accPrec)}}
\newcommand\xcSEOneHamVal{\fpeval{round(0.9853120000000001,\accPrec)}}
\newcommand\xcSEOneHamTest{\fpeval{round(0.9933530805687205,\accPrec)}}

@@

\newcommand\xsOneEigTrain{\fpeval{round(0.9751985611510792,\accPrec)}}
\newcommand\xsOneEigVal{\fpeval{round(0.9533083600000001,\accPrec)}}
\newcommand\xsOneEigTest{\fpeval{round(0.7313738151658769,\accPrec)}}
\newcommand\xsOneHamTrain{\fpeval{round(0.9930935251798562,\accPrec)}}
\newcommand\xsOneHamVal{\fpeval{round(0.9905759999999999,\accPrec)}}
\newcommand\xsOneHamTest{\fpeval{round(0.9855568720379146,\accPrec)}}

@@

\newcommand\xsOOneEigTrain{\fpeval{round(0.807853597122302,\accPrec)}}
\newcommand\xsOOneEigVal{\fpeval{round(0.6941595600000001,\accPrec)}}
\newcommand\xsOOneEigTest{\fpeval{round(0.5419954976303317,\accPrec)}}
\newcommand\xsOOneHamTrain{\fpeval{round(0.9919424460431654,\accPrec)}}
\newcommand\xsOOneHamVal{\fpeval{round(0.7088179999999998,\accPrec)}}
\newcommand\xsOOneHamTest{\fpeval{round(0.4797630331753555,\accPrec)}}

@@

\newcommand\xsSOOneEigTrain{\fpeval{round(0.96949190647482,\accPrec)}}
\newcommand\xsSOOneEigVal{\fpeval{round(0.9456364800000001,\accPrec)}}
\newcommand\xsSOOneEigTest{\fpeval{round(0.7818372037914694,\accPrec)}}
\newcommand\xsSOOneHamTrain{\fpeval{round(0.9875539568345324,\accPrec)}}
\newcommand\xsSOOneHamVal{\fpeval{round(0.9853839999999998,\accPrec)}}
\newcommand\xsSOOneHamTest{\fpeval{round(0.9398933649289098,\accPrec)}}

%ssh2
\newcommand\sshTwoTrainNHam{2761}
\newcommand\sshTwoTrainFracHam{\fpeval{round(\sshTwoTrainNHam/\nHam*100,\nPrec)}}
\newcommand\sshTwoValNHam{2760}
\newcommand\sshTwoValFracHam{\fpeval{round(\sshTwoValNHam/\nHam*100,\nPrec)}}
\newcommand\sshTwoTrainPlusValNHam{\fpeval{\sshTwoTrainNHam+\sshTwoValNHam}}
\newcommand\sshTwoTestNHam{1040}
\newcommand\sshTwoTestFracHam{\fpeval{round(\sshTwoTestNHam/\nHam*100,\nPrec)}}

\newcommand\sshTwoTrainPlusValWindMinusOneNHam{988} %number of winding = -1 in train+val set
\newcommand\sshTwoTrainPlusValWindMinusOneFracHam{\fpeval{round(\sshTwoTrainPlusValWindMinusOneNHam/\sshTwoTrainPlusValNHam*100,\nPrec)}}
\newcommand\sshTwoTrainPlusValWindZeroNHam{1795} %number of winding = 0 in train+val set
\newcommand\sshTwoTrainPlusValWindZeroFracHam{\fpeval{round(\sshTwoTrainPlusValWindZeroNHam/\sshTwoTrainPlusValNHam*100,\nPrec)}}
\newcommand\sshTwoTrainPlusValWindOneNHam{1781}  %number of winding = 1 in train+val set
\newcommand\sshTwoTrainPlusValWindOneFracHam{\fpeval{round(\sshTwoTrainPlusValWindOneNHam/\sshTwoTrainPlusValNHam*100,\nPrec)}}
\newcommand\sshTwoTrainPlusValWindTwoNHam{957}   %number of winding = 2 in train+val set
\newcommand\sshTwoTrainPlusValWindTwoFracHam{\fpeval{round(\sshTwoTrainPlusValWindTwoNHam/\sshTwoTrainPlusValNHam*100,\nPrec)}}

\newcommand\sshTwoTestWindMinusOneNHam{312} %number of winding = -1 in test set
\newcommand\sshTwoTestWindZeroNHam{95} %number of winding = 0 in test set
\newcommand\sshTwoTestWindOneNHam{109}  %number of winding = 1 in test set
\newcommand\sshTwoTestWindTwoNHam{343}   %number of winding = 2 in test set 
\newcommand\sshTwoTestWindMinusOneFracHam{\fpeval{round(\sshTwoTestWindMinusOneNHam/(\sshTwoTestWindMinusOneNHam+\sshTwoTestWindZeroNHam+\sshTwoTestWindOneNHam+\sshTwoTestWindTwoNHam)*100,\nPrec)}}
\newcommand\sshTwoTestWindZeroFracHam{\fpeval{round(\sshTwoTestWindZeroNHam/(\sshTwoTestWindMinusOneNHam+\sshTwoTestWindZeroNHam+\sshTwoTestWindOneNHam+\sshTwoTestWindTwoNHam)*100,\nPrec)}}
\newcommand\sshTwoTestWindOneFracHam{\fpeval{round(\sshTwoTestWindOneNHam/(\sshTwoTestWindMinusOneNHam+\sshTwoTestWindZeroNHam+\sshTwoTestWindOneNHam+\sshTwoTestWindTwoNHam)*100,\nPrec)}}
\newcommand\sshTwoTestWindTwoFracHam{\fpeval{round(\sshTwoTestWindTwoNHam/(\sshTwoTestWindMinusOneNHam+\sshTwoTestWindZeroNHam+\sshTwoTestWindOneNHam+\sshTwoTestWindTwoNHam)*100,\nPrec)}}

\newcommand\sshTwoEigenTrainAcc{0.999655849329953}       % eigenvector training accuracy
\newcommand\sshTwoEigenValAcc{0.9708922101449275}         % eigenvector val accuracy
\newcommand\sshTwoEigenTestAcc{0.6634109429569267}        % eigenvector test accuracy
\newcommand\sshTwoHamTrainAcc{1.0}             % Hamiltonian training accuracy
\newcommand\sshTwoHamValAcc{0.9972499999999997}               % Hamiltonian val accuracy
\newcommand\sshTwoHamTestAcc{0.879697322467986}          % Hamiltonian test accuracy

%%% ssh2 baseline accuracy
\newcommand\sshTwoHamTestBaseline{\fpeval{round(\sshTwoTestWindTwoNHam/(\sshTwoTestWindMinusOneNHam+\sshTwoTestWindZeroNHam+\sshTwoTestWindOneNHam+\sshTwoTestWindTwoNHam),\accPrec)}}
%%% x2 features table entries 
\newcommand\xTwo{$X_2$}
\newcommand\xTwoEigTrain{\fpeval{round(0.999655849329953,\accPrec)}}
\newcommand\xTwoEigVal{\fpeval{round(0.9708922101449275,\accPrec)}}
\newcommand\xTwoEigTest{\fpeval{round(0.6634109429569267,\accPrec)}}
\newcommand\xTwoHamTrain{\fpeval{round(1.0,\accPrec)}}
\newcommand\xTwoHamVal{\fpeval{round(0.9972499999999997,\accPrec)}}
\newcommand\xTwoHamTest{\fpeval{round(0.879697322467986,\accPrec)}}

%%% x_S2 features table entries  
\newcommand\xSTwo{$X_{\mathcal{S}_2}$}
\newcommand\xSTwoEigTrain{\fpeval{round(0.9996107207533504,\accPrec)}}
\newcommand\xSTwoEigVal{\fpeval{round(0.9589830072463768,\accPrec)}}
\newcommand\xSTwoEigTest{\fpeval{round(0.6168351571594877,\accPrec)}}
\newcommand\xSTwoHamTrain{\fpeval{round(1.0,\accPrec)}}
\newcommand\xSTwoHamVal{\fpeval{round(0.9961050724637681,\accPrec)}}
\newcommand\xSTwoHamTest{\fpeval{round(0.8625611175785797,\accPrec)}}
%%% x^c_2 features table entries  
\newcommand\xcTwo{$\hat{X}^c_2$}
\newcommand\xcTwoEigTrain{\fpeval{round(0.9996471930459978,\accPrec)}}
\newcommand\xcTwoEigVal{\fpeval{round(0.9740357971014493,\accPrec)}}
\newcommand\xcTwoEigTest{\fpeval{round(0.6895051222351573,\accPrec)}}
\newcommand\xcTwoHamTrain{\fpeval{round(1.0,\accPrec)}}
\newcommand\xcTwoHamVal{\fpeval{round(0.9976050724637681,\accPrec)}}
\newcommand\xcTwoHamTest{\fpeval{round(0.8862281722933641,\accPrec)}}
%%% x^cE_2 features table entries  
\newcommand\xcETwo{$\hat{X}^c_{\mathcal{E}_2}$}
\newcommand\xcETwoEigTrain{\fpeval{round(0.99943379210431,\accPrec)}}
\newcommand\xcETwoEigVal{\fpeval{round(0.8989626449275362,\accPrec)}}
\newcommand\xcETwoEigTest{\fpeval{round(0.5356883585564609,\accPrec)}}
\newcommand\xcETwoHamTrain{\fpeval{round(1.0,\accPrec)}}
\newcommand\xcETwoHamVal{\fpeval{round(0.9954927536231883,\accPrec)}}
\newcommand\xcETwoHamTest{\fpeval{round(0.7896856810244468,\accPrec)}}

>>>>

%\documentclass[aps,prb,amsmath,twocolumn,amssymb,titlepage]{revtex4-1}
\documentclass[10pt]{revtex4-1}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{nicefrac}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{amsmath} 
\usepackage{subfigure}
\usepackage{multirow} 
\usepackage{tabularx} 
\usepackage{array}
\usepackage{units}
\usepackage{tensor} 
\usepackage{braket}
\usepackage{bm}
\usepackage{hyperref}
\usepackage[resetlabels, labeled]{multibib}
\usepackage{xcolor}
\usepackage{bbm}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Some macros for mathematicall notation %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\newcommand{\hc}{^{\dagger}}
\newcommand{\ad}{\operatorname{{\mathrm ad}}}
\newcommand{\adn}{\ad_{\hat n}}
\newcommand{\adx}{\ad_{\hat x}}
\newcommand{\adX}[1][]{\ad_{\hat {\mathbf{X}}_{#1}}}
\newcommand{\adp}{\ad_{\hat p}}
\newcommand{\calD}{\mathcal{D}}    %Caligraphic D
\newcommand{\inbk}[1]{\left[ #1 \right]}
\newcommand{\inbr}[1]{\left\{ #1 \right\}}
\newcommand{\inp}[1]{\left( #1 \right)}
\newcommand{\pd}{\partial}
\newcommand{\pdf}[3]{\frac{\pd^{#1} #2}{\pd #3^{#1}}} %Partial derivative
\newcommand{\fdf}[3][]{\frac{\delta^{#1} #2}{\delta #3^{#1}}} %Functional derivative 
\newcommand{\indicator}[1]{\mathbbm{1}_{\mathcal{#1}}} % Indicator function

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Macros for section III. Numerical Experiments %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand\nHam{6561}  % total number of hamiltonians
\newcommand\epsilonValue{0.01}  % epsilon criterium for test set
\newcommand\nExp{100}   % number of experiments
%%%% experiment 1
\newcommand\sshOneTestNHam{1005}
\newcommand\sshOneTestFracHam{15.32}
\newcommand\sshOneTrainPlusValNHam{5556}
\newcommand\sshOneTrainNHam{556}
\newcommand\sshOneTrainFracHam{8.47}
\newcommand\sshOneValNHam{5000}
\newcommand\sshOneValFracHam{76.21}
\newcommand\sshOneTrainPlusValWindZeroFracHam{50.79}
\newcommand\sshOneTrainPlusValWindOneFracHam{49.21}
\newcommand\sshOneTestWindZeroFracHam{44.79}
\newcommand\sshOneTestWindOneFracHam{55.21}
\newcommand\sshOneHamTestBaseline{0.5521}
%%%% experiment 2
\newcommand\nEst{25}   % number of estimators in random forest
\newcommand\sshTwoTestNHam{1040}
\newcommand\sshTwoTestFracHam{15.85}
\newcommand\sshTwoTrainPlusValNHam{5521}
\newcommand\sshTwoTrainNHam{2761}
\newcommand\sshTwoTrainFracHam{42.08}
\newcommand\sshTwoValNHam{2760}
\newcommand\sshTwoValFracHam{42.07}
\newcommand\sshTwoTrainPlusValWindMinusOneFracHam{17.90}
\newcommand\sshTwoTrainPlusValWindZeroFracHam{32.51}
\newcommand\sshTwoTrainPlusValWindOneFracHam{32.26}
\newcommand\sshTwoTrainPlusValWindTwoFracHam{17.33}
\newcommand\sshTwoTestWindMinusOneFracHam{36.32}
\newcommand\sshTwoTestWindZeroFracHam{11.06}
\newcommand\sshTwoTestWindOneFracHam{12.69}
\newcommand\sshTwoTestWindTwoFracHam{39.93}
\newcommand\sshTwoHamTestBaseline{0.3993}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Macros for section IV. Information Entropy Signatures %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand\sitesExpOne{(0, 1, 3, 50, 51, 53)}
\newcommand\sitesExpTwo{(0, 1, 2, 3, 4, 5, 46, 48, 49, 50, 51, 53, 94, 95, 96, 97, 98, 99)}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Macros for section V. Topological Feature Engineering And Lattice Compression  %%%%%%%%%%%%%%%%%%%%%%%%
%%% ssh1 lattice sites
\newcommand\sitesSOne{(0, 1, 3, 50)}
\newcommand\sitesEOne{(1, 2, 36, 49)}
\newcommand\sitesOOne{(0, 18, 28, 30)}
%%% ssh2 lattice sites
\newcommand\sitesSTwo{(0, 1, 2, 3, 4, 5, 6, 7, 46, 48, 49, 50)}
\newcommand\sitesETwo{(0, 1, 2, 3, 4, 5, 6, 7, 47, 48, 49, 50)}
\newcommand\sitesOTwo{(0, 1, 2, 3, 4, 5, 43, 44, 45, 46, 47, 48)}
%%% feature names
\newcommand\xalpha{$X_\alpha$}
\newcommand\xSalpha{$X_{\mathcal{S}_\alpha}$}
\newcommand\xcalpha{$\hat{X}^c_\alpha$}
\newcommand\xcEalpha{$\hat{X}^c_{\mathcal{E}_\alpha}$}
\newcommand\xcSEalpha{$\hat{X}^c_{\mathcal{S}_\alpha,\mathcal{E}_\alpha}$}
\newcommand\xsalpha{$\hat{X}^s_\alpha$}
\newcommand\xsOalpha{$\hat{X}^s_{\mathcal{O}_\alpha}$}
\newcommand\xsSOalpha{$\hat{X}^s_{\mathcal{S}_\alpha,\mathcal{O}_\alpha}$}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Macros for table %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand{\tableRow}[1]{\\[#1 cm]}
\newcommand{\tableRowHeader}[1]{\\[#1 cm]}
\newcommand\tableRowHeaderEnd{\tableRowHeader{0.3}}
\newcommand\tableRowEnd{\tableRow{0.15}}
%%% table columns
\newcommand\SSHSys{SSH system}         
\newcommand\Feat{Features}              
\newcommand\ValEig{Val. eigenvectors}   
\newcommand\TestEig{Test eigenvectors}  
\newcommand\ValHam{Val. Hamiltonians}   
\newcommand\TestHam{Test Hamiltonians}  

@@

\newcommand\xOneEigTrain{0.9814}
\newcommand\xOneEigVal{0.9639}
\newcommand\xOneEigTest{0.7897}
\newcommand\xOneHamTrain{1.000}
\newcommand\xOneHamVal{1.000}
\newcommand\xOneHamTest{0.9919}

@@

\newcommand\xSOneEigTrain{0.9700}
\newcommand\xSOneEigVal{0.9444}
\newcommand\xSOneEigTest{0.7763}
\newcommand\xSOneHamTrain{0.9880}
\newcommand\xSOneHamVal{0.9853}
\newcommand\xSOneHamTest{0.9905}

@@

\newcommand\xcOneEigTrain{0.9753}
\newcommand\xcOneEigVal{0.9521}
\newcommand\xcOneEigTest{0.7374}
\newcommand\xcOneHamTrain{0.9983}
\newcommand\xcOneHamVal{0.9976}
\newcommand\xcOneHamTest{0.9916}

@@

\newcommand\xcEOneEigTrain{0.9755}
\newcommand\xcEOneEigVal{0.8280}
\newcommand\xcEOneEigTest{0.6067}
\newcommand\xcEOneHamTrain{0.9985}
\newcommand\xcEOneHamVal{0.9979}
\newcommand\xcEOneHamTest{0.9191}

@@

\newcommand\xcSEOneEigTrain{0.9701}
\newcommand\xcSEOneEigVal{0.9444}
\newcommand\xcSEOneEigTest{0.8176}
\newcommand\xcSEOneHamTrain{0.9882}
\newcommand\xcSEOneHamVal{0.9853}
\newcommand\xcSEOneHamTest{0.9934}

@@

\newcommand\xsOneEigTrain{0.9752}
\newcommand\xsOneEigVal{0.9533}
\newcommand\xsOneEigTest{0.7314}
\newcommand\xsOneHamTrain{0.9931}
\newcommand\xsOneHamVal{0.9906}
\newcommand\xsOneHamTest{0.9856}

@@

\newcommand\xsOOneEigTrain{0.8079}
\newcommand\xsOOneEigVal{0.6942}
\newcommand\xsOOneEigTest{0.5420}
\newcommand\xsOOneHamTrain{0.9919}
\newcommand\xsOOneHamVal{0.7088}
\newcommand\xsOOneHamTest{0.4798}

@@

\newcommand\xsSOOneEigTrain{0.9695}
\newcommand\xsSOOneEigVal{0.9456}
\newcommand\xsSOOneEigTest{0.7818}
\newcommand\xsSOOneHamTrain{0.9876}
\newcommand\xsSOOneHamVal{0.9854}
\newcommand\xsSOOneHamTest{0.9399}
%%% x2 features table entries 
\newcommand\xTwo{$X_2$}
\newcommand\xTwoEigTrain{0.9997}
\newcommand\xTwoEigVal{0.9709}
\newcommand\xTwoEigTest{0.6634}
\newcommand\xTwoHamTrain{1.000}
\newcommand\xTwoHamVal{0.9972}
\newcommand\xTwoHamTest{0.8797}
%%% x_S2 features table entries  
\newcommand\xSTwo{$X_{\mathcal{S}_2}$}
\newcommand\xSTwoEigTrain{0.9996}
\newcommand\xSTwoEigVal{0.9590}
\newcommand\xSTwoEigTest{0.6168}
\newcommand\xSTwoHamTrain{1.000}
\newcommand\xSTwoHamVal{0.9961}
\newcommand\xSTwoHamTest{0.8626}
%%% x^c_2 features table entries  
\newcommand\xcTwo{$\hat{X}^c_2$}
\newcommand\xcTwoEigTrain{0.9996}
\newcommand\xcTwoEigVal{0.9740}
\newcommand\xcTwoEigTest{0.6895}
\newcommand\xcTwoHamTrain{1.000}
\newcommand\xcTwoHamVal{0.9976}
\newcommand\xcTwoHamTest{0.8862}
%%% x^cE_2 features table entries  
\newcommand\xcETwo{$\hat{X}^c_{\mathcal{E}_2}$}
\newcommand\xcETwoEigTrain{0.9994}
\newcommand\xcETwoEigVal{0.8990}
\newcommand\xcETwoEigTest{0.5357}
\newcommand\xcETwoHamTrain{1.000}
\newcommand\xcETwoHamVal{0.9955}
\newcommand\xcETwoHamTest{0.7897}
%%% x^cSE_2 features table entries  
\newcommand\xcSETwo{$\hat{X}^c_{\mathcal{S}_2,\mathcal{E}_2}$}
\newcommand\xcSETwoEigTrain{0.9994}
\newcommand\xcSETwoEigVal{0.8999}
\newcommand\xcSETwoEigTest{0.5030}
\newcommand\xcSETwoHamTrain{1.000}
\newcommand\xcSETwoHamVal{0.9956}
\newcommand\xcSETwoHamTest{0.7671}
%%% x^s_2 features table entries  
\newcommand\xsTwo{$\hat{X}^s_2$}
\newcommand\xsTwoEigTrain{0.9997}
\newcommand\xsTwoEigVal{0.9735}
\newcommand\xsTwoEigTest{0.6878}
\newcommand\xsTwoHamTrain{1.000}
\newcommand\xsTwoHamVal{0.9971}
\newcommand\xsTwoHamTest{0.8899}
%%% x^SO_2 features table entries  
\newcommand\xsOTwo{$\hat{X}^s_{\mathcal{O}_2}$}
\newcommand\xsOTwoEigTrain{0.9994}
\newcommand\xsOTwoEigVal{0.9042}
\newcommand\xsOTwoEigTest{0.5527}
\newcommand\xsOTwoHamTrain{1.000}
\newcommand\xsOTwoHamVal{0.9918}
\newcommand\xsOTwoHamTest{0.7427}
%%% x^SSO_2 features table entries  
\newcommand\xsSOTwo{$\hat{X}^s_{\mathcal{S}_2,\mathcal{O}_2}$}
\newcommand\xsSOTwoEigTrain{0.9992}
\newcommand\xsSOTwoEigVal{0.8204}
\newcommand\xsSOTwoEigTest{0.4127}
\newcommand\xsSOTwoHamTrain{1.000}
\newcommand\xsSOTwoHamVal{0.9942}
\newcommand\xsSOTwoHamTest{0.5903}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Figures for Main article %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% phase diagrams (figure 1)
%\newcommand\phaseDiagramsFigs{./00_article/phase_diagrams/}
\newcommand\SSHOnePhaseDiagram{./ssh1_phase_diagram.png}
\newcommand\SSHTwoPhaseDiagram{./ssh2_phase_diagram.png}
%%% ssh1 experiments (figure 2)
%\newcommand\SSHOneExperimentsFigs{./00_article/ssh1/real_space_all_sites/}
\newcommand\SSHOneTrainValTestSplit{./ssh1_scatter_train_val_test_experiment_0.png}
\newcommand\SSHOneWindingTrain{./ssh1_scatter_winding_train_experiment_0.png}
\newcommand\SSHOnePredictionGrid{./ssh1_pcolormesh_prediction_grid_experiment_0.png}
%%% ssh2 experiments (figure 3)
%\newcommand\SSHTwoExperimentsFigs{./00_article/ssh2/real_space_all_sites/}
\newcommand\SSHTwoTrainValTestSplit{./ssh2_scatter_train_val_test_experiment_0.png}
\newcommand\SSHTwoWindingTrain{./ssh2_scatter_winding_train_experiment_0.png}
\newcommand\SSHTwoPredictionGrid{./ssh2_pcolormesh_prediction_grid_experiment_0.png}
%%% ssh1 probability heatmaps  (figure 4)
\newcommand\SSHOneWindingZero{./ssh1_imshow_winding_grid_winding_0_sim.png}
\newcommand\SSHOneWindingOne{./ssh1_imshow_winding_grid_winding_1_sim.png}
\newcommand\SSHOneHeatmap{./ssh1_merge_imshow_winding_grids_second_sim.png}
%%% ssh2 probability heatmaps  (figure 5)
\newcommand\SSHTwoWindingMinusOne{./ssh2_imshow_winding_grid_winding_-1_sim.png}
\newcommand\SSHTwoWindingZero{./ssh2_imshow_winding_grid_winding_0_sim.png}
\newcommand\SSHTwoWindingOne{./ssh2_imshow_winding_grid_winding_1_sim.png}
\newcommand\SSHTwoWindingTwo{./ssh2_imshow_winding_grid_winding_2_sim.png}
\newcommand\SSHTwoHeatmap{./ssh2_merge_imshow_winding_grids_sim.png}
%%% information entropy signatures (figure 6)
\newcommand\SSHOneEntropySignature{./ssh1_plot_feature_importances.png}
\newcommand\SSHTwoEntropySignature{./ssh2_plot_feature_importances.png}
